Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
Todo notes
typo

\TheDeterminismChecker is also capable of detecting nondetermism in test cases. We provide a stub file
for \<junit> in which we annotated all the \<assert> methods as accepting only \<Det> parameters.
This will report any \<junit> test that passes nondeterministic arguments to \<assert>s and the test doesn't
even have to be executed in our case.
\todo{It took one of our authors about an hour to create this stub file - proof of easy estensibility of tool?} 
\todo{Link to det checker repo?}

@@

>>>>

\TheDeterminismChecker is also capable of detecting nondetermism in test cases. We provide a stub file
for \<junit> in which we annotated all the \<assert> methods as accepting only \<Det> parameters.
This will report any \<junit> test that passes nondeterministic arguments to \<assert>s and the test doesn't
even have to be executed in our case.
\todo{It took one of our authors about an hour to create this stub file - proof of easy extensibility of tool?} 
\todo{Link to det checker repo?}

@@

\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.
